Naming Anonymous JavaScript Functions

### 2011-04-12 papers/splash-wavefront2011/sigplanconf-template.tex
section 2 is updated.

\lstset{basicstyle=\scriptsize}
\lstset{emph={FOO,BAR}} %,emphstyle=\bf}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new, this}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {          // main
10   var foo = new FOO(            
11      function(){                 // main/foo<
12        this.welcome = "Hi!";
13      });
14   var bar = new BAR("GoodBye.");
15   alert(foo.welcome);
16   alert(bar.message);
17 };
18 var FOO = function(){            // FOO<    
19   var instances;
20   return function(initializer){  // FOO
21       instances++;         
22       initializer.apply(this);
23     }
24 }();
25 var BAZ = BAR = function(msg){   // BAR
26   this.message = msg;
27 }
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.jpg}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

@@

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{FOO}} and {\small\texttt{BAR}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{BAZ.BAR}} class for {\small\texttt{bar}} as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{FOO}} and {\small\texttt{BAR}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.jpg}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.jpg}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

@@

The next two functions, {\small\texttt{FOO}} on line 19 and {\small\texttt{BAR}} on line 22 are simple examples of case 6.  The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

>>>>

\lstset{basicstyle=\scriptsize}
\lstset{emph={Foo,Bar}} %,emphstyle=\bf}
\lstdefinelanguage{myLang}
{morekeywords={if, function, var, return, new, this}}

\begin{lstlisting}[frame=single, language=myLang]
9  var main = function() {          // main
10   var foo = new Foo(            
11      function(){                 // main/foo<
12        this.welcome = "Hi!";
13      });
14   var bar = new Bar("GoodBye.");
15   alert(foo.welcome);
16   alert(bar.message);
17 };
18 var Foo = function(){            // Foo<    
19   var instances;
20   return function(initializer){  // Foo
21       instances++;         
22       initializer.apply(this);
23     }
24 }();
25 var Baz = Bar = function(msg){   // Bar
26   this.message = msg;
27 }
\end{lstlisting}
\caption{An excerpt of a JavaScript code.}
\label{js-code}
\end{figure}

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_object_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-objects.png}}
\hfil
\subfigure[Firebug]{\label{fig_object_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-objects.png}}}
\caption{The screenshot of variables view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-objects}
\end{figure*}

@@

Figure~\ref{js-code} shows an excerpt of a JavaScript program we use to illustrate this issue. We set a breakpoint on line 15 and examine the runtime elements at this breakpoint by two JavaScript debuggers, Google Chrome and Firebug (Figure~\ref{debuggers-objects}). Two objects assigned to variables {\small\texttt{foo}} and {\small\texttt{bar}} are constructed by two different constructors: {\small\texttt{Foo}} and {\small\texttt{Bar}}. However, Google Chrome debugger shows the general class of {\small\texttt{Object}} for {\small\texttt{foo}} and the {\small\texttt{Baz.Bar}} class for {\small\texttt{bar}} as their summaries. The first class is very general and the second one is misleading. The developer has to expand the object nodes to recognize their similarities and differences. Firebug classify both objects in the general {\small\texttt{Object}} class, but includes some of the object properties in the summary. These additional properties may hint the developer about the object structures. {\small\texttt{Foo}} and {\small\texttt{Bar}} definitions at lines 20 and 25 explain the debuggers' behavior; the function statements has no explicit name (identifier), therefore debuggers considered them as \textit{anonymous} functions.

@@

\begin{figure*}[htp]
\centerline{
\subfigure[Google Chrome Debugger]{\label{fig_second_case}\includegraphics[width=0.48\textwidth]{pic/chrome-callstack.png}}
\hfil
\subfigure[Firebug]{\label{fig_first_case}\includegraphics[width=.48\textwidth]{pic/fbug-callstack.png}}}
\caption{The screenshot of call-stack view of Google Chrome and Firebug JavaScript debuggers paused on a breakpoint at line 15 of the program shown in Figure~\ref{js-code}.}
\label{debuggers-callstack}
\end{figure*}

@@

The next two functions, {\small\texttt{Foo}} on line 19 and {\small\texttt{Bar}} on line 22 are simple examples of case 6.  The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
